Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
proof read and moved text a bit

This paper is structured as follows.
\AP{TBM}
In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
and describe the method used to identify its molecular gas complexes.
In \Sec{results}, we present scaling relations based on
the MC identified and compare them with observations of molecular
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
We present Toomre stability analysis in \Sec{Q} and
the cumulative mass distribution of the MCs in \flower in \Sec{cmf}.
In \Sec{diss}, we discuss the results and implications of our findings,
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

@@

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
%\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
% (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

% radiative feedback --> NT pressure
Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae and OB/AGB stars to account for energy dissipations. To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell when supernovae explode. The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy. Radiation pressure on the dust and gas is also included (see \citealt{Pallottini17a} for details).

Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}.
Briefly, by \z$\sim$6, \flower is a Lyman-break galaxy (LBG) hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne. It is therefore a prototypical galaxy at \z$\sim$6.

@@

\subsection{Star Formation History} \label{sec:sfh}
One of the advantage of studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
% {\AP potentially moving the following, maybe postpone after structures have been identified as a description? }
% {\DL or maybe in the discussion section?}
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures compared to more evolved galaxies found at 
a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
ones). % mainly expecting differences in alpha_vir, sigma, M_cl.

@@

We show the \SF history of \flower in \Fig{SFH}, where
the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
The SFR plotted in Figure 2 of \citet{Pallottini17b}
is a factor of two higher than shown here since they also include contributions from
massive satellites galaxies within the surrounding $\approx$50\,kpc, which
are accreted onto \flower at \z$\lesssim$\,2.}
as it evolves from an actively accreting phase to
a starburst phase after a major merger, and then back to a relatively quiescent phase
over the few hundred Myr simulated in our simulation.
The SFR of \flower is calculated based on existing young stellar population, which is
defined to have an age of $t_{\rm age}<$\,10\,Myr.

Given the stochasticity in the \SF history of \flower,
we show the scaling relations found for two particular snapshots/evolutionary stages of \flower
as examples in \Sec{singless} to illustrate the salient points of the discussion,
since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
most extreme variations in the cloud dynamics) --- one of which \flower is
actively accreting materials from its surrounding 
and another of which \flower is undergoing
a starburst phase after a major merger (see \Fig{SFH}).

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot, corresponding to the 
accreting phase shown in \Fig{SFH}.
\label{fig:h2density}}
\end{figure}

@@

We show in \Fig{dist} the MC distributions in terms of their
molecular gas masses, radii, and gas mass fractions, which we define as 
\begin{equation}
f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass.
We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified. 
% {\AP  maybe we can tie it to the mass resolution limitation imposed by our criterion.}
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
\caption{
Distributions of masses, sizes, and gas mass fractions of MCs identified using 
the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
Note the scale shown on the y-axes are different between the left and right panels, as less MCs are identified 
at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external thermal pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:alpha}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation), 
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities (see bottom panels of \Fig{alpha16} and 
\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

We use the virial parameter, which is defined using \Eq{alpha} and describes 
the balance between kinetic and gravitational potential energies, 
to quantify how stable an MC is. 
An $\alpha_{\rm vir}\approx$2 corresponds to approximately equipartition between the two energy terms 
and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that 
the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.

@@

%
\AP{I would move the following when discussing the velocity dispersion; additionally, the large velocity dispersions was also noted in Vallini2018a, we can use some of those results to complement the discussion (e.g. shift for the CO sled at higher J then local galaxies).}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
\caption{
Larson's (linewidth-size) relation of \flower in
accreting phase (top) and
starburst phase (bottom) compared to
those observed in nearby and the \z$\sim$2 star-forming galaxy.
% Red lines show the relation obtained from \citet{}.
Literature data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accreting phase (star symbols) compared to those observed in the Milky Way.
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers).
The V-shaped dashed lines show the loci along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accreting phase (see \Sec{sfh})
compared to the 
observational data of molecular clouds in the Milky Way associated with massive \SF 
\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
which we extrapolate to match the mass and size scales of the MCs of \flower.
By comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun) 
in the Milky Way, \citet{Kauffmann10c} report a 
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
at a given radius. As shown in \Fig{MR}, the MCs identified in the accreting phase of \flower lie above this relation, along the locus 
with a visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
% {\AP note that we can directly calculate Av given the dust properties in the galaxy or approximate it as av = cost N * Z con cost assuming a MW-like scaling}
On the other hand, the MCs of \flower lie below the locus of $A_V$\eq100\,mag that the Milky Way clouds follow.
{\bf This may suggest ....}
We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
parameter space as the accreting phase. 
{\bf so...}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accreting phase of \flower in our simulation (star symbols) 
compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
established based on \obs of the Milky Way.
Star symbols are color-coded by increasing $n_{\rm cut}$.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
% \citep{Lombardi10a}.
\label{fig:MR}}
\end{figure*}

\subsubsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites
to test
the robustness of our results against the choice of density threshold by adopting
different sets of $n_{\rm cut}$ in identifying the MCs.
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
dependent on the choice of density thresholds.
We vary the choice of H$_2$ density for each of the snapshots and
find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6
MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of
cloud scaling relations).
In addition, for the densest MC in the main disk of \flower, we find that while
its size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect,
its velocity dispersion remain
approximately $\sigma\simeq$\,200\,\kms (see \Fig{larsons_single}).
This lack of variation is reassuring, in the sense that at least on the scales studied here,
the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
Our results are therefore robust.

@@

\section{Cumulative Mass Distribution}   \label{sec:cmf}

The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun,
consistent with those observed in \z$\sim$2 galaxies in
rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
Observational studies in the nearby Universe, where 
spatially resolution are better at revealing molecular (sub-)structures,
often report the mass distribution of molecular clouds in the form of a cumulative function (CMF).
While the CMF of the MCs for a given snapshot of our simulation is 
quite noisy, since we have only one (main) galaxy, 
we could improve the ``signal-to-noise ratio'' by including 
MCs identified across all snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the 700\,Myr studied here.}.
We show the resulting CMF in \Fig{cmf}.

>>>>

This paper is structured as follows.
\AP{TBM}
In \Sec{sim}, we describe the setup of our simulation and properties of our main galaxy (\flower),
and describe the method used to identify its molecular gas complexes.
In \Sec{results}, we present scaling relations based on
the MC identified and compare them with observations of molecular
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
We present Toomre stability analysis in \Sec{Q}.
In \Sec{diss}, we discuss the results and implications of our findings,
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

@@

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs) seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

% radiative feedback --> NT pressure
Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernovae and OB/AGB stars to account for energy dissipations. To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell during a supernova explosion. The energy dissipated is then injected into the ISM in the form of kinetic and thermal energies. Radiation pressure on the dust and gas is also included (see \citealt{Pallottini17a} for details).

Details on the properties of \flower\ --- the main galaxy in our simulation --- are discussed in \citet{Pallottini17b}.
Briefly, by \z$\sim$6, \flower is a Lyman-break galaxy (LBG), hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne. It is therefore a prototypical galaxy at \z$\sim$\,6.

@@

\subsection{Star Formation History} \label{sec:sfh}
One of the main advantages for studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
% {\AP potentially moving the following, maybe postpone after structures have been identified as a description? }
% {\DL or maybe in the discussion section?}
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures compared to more evolved galaxies found at 
a later cosmic time (e.g., some molecular structures may disperse while others may agglomerate into more massive
ones). % mainly expecting differences in alpha_vir, sigma, M_cl.

@@

We show the \SF history of \flower in \Fig{SFH}, where
the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
The SFR plotted in Figure 2 of \citet{Pallottini17b}
is a factor of two higher than shown here since they also include contributions from
massive satellite galaxies within the surrounding $\approx$50\,kpc, which
are accreted onto \flower at \z$\lesssim$\,2.}
as it evolves from an actively accreting phase to
a starburst phase after a major merger, and then back to a relatively quiescent phase
over the few hundred Myr simulated in our simulation.
The SFR of \flower is calculated based on existing young stellar population, which is
defined to have an age of $t_{\rm age}<$\,10\,Myr.

Given the stochasticity in the \SF history of \flower,
we show the scaling relations found for two particular snapshots/evolutionary stages of \flower
as examples in \Sec{singless} to illustrate the salient points of the discussion presented in this paper,
since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
most extreme variations in the cloud dynamics) --- one of which \flower is
actively accreting materials from its surrounding 
and another of which \flower is undergoing
a starburst phase after a major merger (see \Fig{SFH}).

@@

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot, corresponding to the 
accretion phase shown in \Fig{SFH}.
\label{fig:h2density}}
\end{figure}

@@

We show in \Fig{dist} the MC distributions in terms of their
molecular gas masses, radii, and gas mass fractions, which we define as 
\begin{equation}
f_{\rm gas} = \frac{M_{\rm H2}} {\left(M_{\rm H2} + M_*\right)},
\end{equation}
where $M_*$ is the stellar mass.
We note that the distributions vary for different snapshots, depending on the evolutionary stage of \flower.
The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a ``minimum'' MC mass of
the order of 10$^{6.5}$\,\Msun for the densest MC.
% {\AP  maybe we can tie it to the mass resolution limitation imposed by our criterion.}
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
\caption{
Distributions of mass, size, and gas mass fraction of MCs identified using 
the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
Note that the scale shown on the y-axes are different between the left and right panels, as less MCs are identified 
at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within
a medium of pressure $P$ is described using the virial theorem:
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and
bulk motions), $T_s$ is the surface term due to external pressure,
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure term from velocity dispersion, the second
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure),
the LHS and the last term on the RHS vanish. The equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\label{eqn:alpha}
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere.
We can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to one of the Larson's relations (linewidth-size relation), 
which can be recast into the form of:
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), % external pressure
Equation~\ref{eqn:virial} becomes
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
Therefore, for a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities (see bottom panels of \Fig{alpha16} and 
\Fig{alpha27}).
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$
is in equilibrium with the external pressure $P_{\rm ext}$ (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE, where
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

We use the virial parameter, which is defined using \Eq{alpha} and describes 
the balance between kinetic and gravitational potential energies, 
to quantify how stable an MC is. 
An $\alpha_{\rm vir}\approx$\,2 corresponds to approximately equipartition between the two energy terms 
and is often used to assess the boundedness of a given structure \citep[see e.g., ][]{Kauffmann17b}\footnote{Note, however, that 
the true virial state/boundedness of a given structure also depends on the surface terms and the magnetic field (see \Eq{virial}).}.

@@

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}
\caption{
Larson's (linewidth-size) relation of \flower in
accretion phase (top) and
starburst phase (bottom) compared to
those observed in nearby and the \z$\sim$2 star-forming galaxy.
% Red lines show the relation obtained from \citet{}.
Literature data and empirical relations are compiled from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, Swinbank11a, Leroy15a}.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower in the accretion phase (star symbols) compared to those observed in the Milky Way 
(other symbols).
Literature data are compiled from \citealt{Kauffmann17b} and references therein.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of the MCs identified in our simulation (star symbols) 
compared to those observed in the Milky Way (black dot markers; \citealt{Heyer09a}).
The V-shaped dashed lines show the loci along which the given external pressures
are needed for MCs to have linewidth $\sigma$ for a given set of surface densities (see \Sec{PVE}).
In both panels, the star symbols are color-coded by $n_{\rm cut}$.
Star symbols lying close to $\alpha_{\rm vir}\approx2$ in the top panel  
and the locus of $\log{(P/\textrm{K cm}^{-3}) = 6}$ in the bottom panel correspond to MCs identified in the satellite galaxies.
\label{fig:alpha16}}
\end{figure*}

@@

We show in \Fig{MR} the size-mass relation of the MCs of \flower in the accretion phase (see \Sec{sfh})
compared to the 
observational data of molecular clouds in the Milky Way associated with massive \SF 
\citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained based on 
Milky Way data (\citealt{Kauffmann10b, Kauffmann10c} and references therein),
which we extrapolate to match the mass and size scales of the MCs of \flower.
By comparing the masses and sizes found in clouds with and without massive \SF ($<$10\,\Msun) 
in the Milky Way, \citet{Kauffmann10c} report a 
mass-size relation of $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$ as the threshold for massive \SF. 
That is, cluster-forming cloud fragments are found to be more massive than those that are devoid of clusters 
at a given radius. As shown in \Fig{MR}, the MCs identified in the accretion phase of \flower lie above this relation, along the locus 
with a visual extinction of $A_V$\eq4\,mag. {\bf This may suggest ....}
% {\AP note that we can directly calculate Av given the dust properties in the galaxy or approximate it as av = cost N * Z con cost assuming a MW-like scaling}
On the other hand, the MCs of \flower lie below the locus of $A_V$\eq100\,mag that the Milky Way clouds follow.
{\bf This may suggest ....}
We also examine the size-mass relation of the MCs identified in other snapshots, finding that they lie in the same 
parameter space as the accretion phase. 
{\bf so...}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) 
compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
established based on \obs of the Milky Way.
Star symbols are color-coded by increasing $n_{\rm cut}$.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
% \citep{Lombardi10a}.
\label{fig:MR}}
\end{figure*}

\subsubsection{Cumulative Mass Distribution}   \label{sec:cmf}

The mass range of the MCs identified in our simulation is $M_{\rm cl}\approx$10$^{6.5-9}$\,\Msun,
consistent with those observed in \z$\sim$2 galaxies in
rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}.
Observational studies in the nearby Universe, where 
spatially resolution are better at revealing molecular (sub-)structures,
often report the mass distribution of molecular clouds in the form of a cumulative function (CMF).
While the CMF of the MCs for a given snapshot of our simulation is 
quite noisy, since we have only one (main) galaxy, 
we can improve the ``signal-to-noise ratio'' by including 
MCs identified across all snapshots\footnote{This approach is valid unless in some snapshots,
the galaxy experience a violent event, which is relatively rare across the 700\,Myr studied here.}.
We show the resulting CMF in \Fig{cmf}.

Motivated by the observational study by \citealt{Blitz07a}, we fit a power-law to the CMF, which is expressed in the form of:
\begin{equation}
n\left(M^\prime > M\right) \propto M_{\rm cl}^\alpha,
\end{equation}
where $n$ is the number of MCs with masses exceeding $M_{\rm cl}$ and $\alpha$ is the power-law index.
We find that 
the slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for the lowest and the highest $n_{\rm cut}$ adopted.
The uncertainties are the formal fitting uncertainties.
Regardless of the density threshold adopted, the slope of the CMF of \flower (\Fig{cmf})
is shallower compared to those observed in nearby galaxies (between $-$1.6 and $-$2.5; based on a sample of
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}). % between -1.6 to -2.5, mostly -1.7, except for M33, which is -2.5
This suggests that the MCs of \flower are more massive compared to those observed in the nearby Universe.

@@
